Testing Gravity using Type Ia Supernovae Discovered by LSST

### 2018-09-16 doc/article.tex
making progress

\author{and others}

@@

\section{Introduction}
Peculiar velocities provide a measure of $f\sigma_8$, which in turn probes gravity.  As precise distance indicators Type~Ia supernovae
can provide precise peculiar velocities (expressed practically in term of peculiar magnitudes)
of their host galaxies \citep{2006PhRvD..73l3526H,2011ApJ...741...67D}.
\citet{2015JCAP...12..033H, 2017JCAP...05..015H}  test and ultimately find consistency between
$\Lambda$CDM and the peculiar velocities of existing SN~Ia samples.

@@

\section{Simulated Data}
The Buzzard (v1.6) galaxy catalog is used.  This is because it is the survey, among those currently available
in the Generic Catalog Reader of the DESC, with a light cone that covers the largest solid angle of 10,313.24 sq.~deg.  However,
the survey geometry is different
from that of LSST.  The catalog is based on a Flat $\Lambda$CDM model with $\Omega_M=0.286$, $\Omega_B=0.047$, and
$\Omega_\nu=0$,
The catalog contains140M galaxies with observed $z<0.2$ for which the star formation rate and stellar mass are available; from these  parameters the
supernova rate of each host is determined using the rates of
\citet{2012ApJ...755...61S}.  Supernovae are realized for a span of 10 observer-years yielding 17,205 objects.  This total supernova
production underestimates the expected discovery of 134,574 supernovae in 10 observer-years based on the volumetric
rate of \citet{2010ApJ...713.1026D}.  The volumetric rate is more robust, so the sample under consideration in this article
corresponds to 1.3 years worth of discoveries.

\section{Analysis}
The analysis of this article is identical to that of \citet{2015JCAP...12..033H, 2017JCAP...05..015H}.   The peculiar magnitude correlation
function $\xi_{\delta m \delta m}$ expected from General Relativity, the matter density power spectrum at the CMB assuming the same
cosmological parameters used for the Buzzard catalog, is calculated using CAMB \citep{Lewis:2002ah}.  Our model for the data covariance
is
\begin{equation}
C_{ij} = A\xi_{\delta m \delta m}(\mathbf{r_i},\mathbf{r_j}) + \frac{\sigma_M^2}{N_i} \delta_{ij}.
\end{equation}
In this model, we treat the shape of the power spectrum $\xi$ as fixed, and use the parameter $A$ to represent
deviations from General Relativity $A=1$.  This model is not sensitive to  the shape of
the power spectrum between gravitational models.  Nevertheless, for
convenience we make the association that our model gives $f\sigma_8 = A f\sigma_8^{GR}$, where $ f\sigma_8^{GR}$ is the expectation
from General Relativity.  Special cases of modified gravity could give $A=1$, while inconsistency with $A=1$ is inconsistency with GR.

>>>>

\author{others}

@@

\section{Introduction}
Peculiar velocities provide a measure of $f\sigma_8$, which in turn probes gravity.  As precise distance indicators Type~Ia supernovae
can provide precise peculiar velocities (expressed equivalently as peculiar magnitudes)
of their host galaxies \citep{2006PhRvD..73l3526H,2011ApJ...741...67D}.
\citet{2015JCAP...12..033H, 2017JCAP...05..015H}  test and ultimately find consistency between
$\Lambda$CDM and the peculiar velocities of existing SN~Ia samples.

@@

\section{Simulated Data}
The Buzzard (v1.6) galaxy catalog is used.  This is because it is the survey, among those currently available
in the Generic Catalog Reader of the DESC, with a light cone that covers the largest solid angle of 10,313.24 sq.~deg.  However,
the survey geometry is different
from that of LSST.  The catalog is based on a Flat $\Lambda$CDM model with $\Omega_M=0.286$, $\Omega_B=0.047$, and
$\Omega_\nu=0$,
The catalog contains140M galaxies with observed $z<0.2$.  Each galaxies cosmological redshift, redshift that combines
which the star formation rate and stellar mass are available; from these  parameters the
supernova rate of each host is determined using the rates of
\citet{2012ApJ...755...61S}.  Supernovae are realized for a span of 10 observer-years yielding 17,205 objects.  This total supernova
production underestimates the expected discovery of 134,574 supernovae in 10 observer-years based on the volumetric
rate of \citet{2010ApJ...713.1026D}.  The volumetric rate is more robust, so the sample under consideration in this article
corresponds to 1.3 years worth of discoveries.

\section{Analysis}
The analysis of this article is identical to that of \citet{2015JCAP...12..033H, 2017JCAP...05..015H}.   The peculiar magnitude correlation
function $\xi_{\delta m \delta m}$ expected from General Relativity, the matter density power spectrum at the CMB assuming the same
cosmological parameters used for the Buzzard catalog, is calculated using CAMB \citep{Lewis:2002ah}.  Our model for the data covariance
is
\begin{equation}
C_{ij} = A\xi_{\delta m \delta m}(\mathbf{r_i},\mathbf{r_j}) + \frac{\sigma_M^2}{N_i} \delta_{ij}.
\end{equation}
In this model, we treat the shape of the power spectrum $\xi$ as fixed, and use the parameter $A$ to represent
deviations from General Relativity $A=1$.  This model is not sensitive to  the shape of
the power spectrum between gravitational models.  Nevertheless, for
convenience we make the association that our model gives $f\sigma_8 = A f\sigma_8^{GR}$, where $ f\sigma_8^{GR}$ is the expectation
from General Relativity.  Special cases of modified gravity could give $A=1$, but inconsistency with $A=1$ is is evidence against General Relativity.
